An Empirical Study of Invasion and Resistance for Iterated Prisoner's Dilemma Strategies

### 2017-05-14 main.tex
Fix broken fig ref.

\begin{figure}[!hbtp]
    \centering
    \input{./tex/fsm_one.tex}
    \caption{TF1: a 16 state finite state machine.}
    \label{fig:tf1}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \input{./tex/fsm_two.tex}
    \caption{TF2: a 16 state finite state machine.}
    \label{fig:tf2}
\end{figure}

@@

Figure~\ref{fig:correlation_coeficients} show the correlation coefficients
of the ranks of strategies in differing population size. It is immediate to
note that how well a strategy performs in any Moran process for \(N>2\) has
little to do with the performance for \(N=2\). This illustrates why the strong
performance of Zero determinant strategies predicted in \cite{Press2012} does
not extend to larger populations. This was discussed theoretically in
\cite{Adami2013} however not observed empirically at the scale presented here.

>>>>

\begin{figure}[!hbtp]
    \centering
    \input{./tex/fsm_one.tex}
    \caption{TF1: a 16 state finite state machine with a handshake leading to
    mutual cooperation at state 4.}
    \label{fig:tf1}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \input{./tex/fsm_two.tex}
    \caption{TF2: a 16 state finite state machine with a handshake leading to
    mutual cooperation at state 16.}
    \label{fig:tf2}
\end{figure}

@@

Figure~\ref{fig:correlation_coefficients} show the correlation coefficients
of the ranks of strategies in differing population size. It is immediate to
note that how well a strategy performs in any Moran process for \(N>2\) has
little to do with the performance for \(N=2\). This illustrates why the strong
performance of Zero determinant strategies predicted in \cite{Press2012} does
not extend to larger populations. This was discussed theoretically in
\cite{Adami2013} however not observed empirically at the scale presented here.
